Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-03-14 WSSSPE4_report/wg_access.tex
clarify & links to Google Group

%Introduction to group here, including the overall objective of work in this area.
Each developer of software with uncommon needs (hardware, software, libraries, data sets) or non-public code must acquire, setup, and maintain their own continuous integration systems.  For example, software groups that develop BIOUNO, CI4SI, GROMACS) have done this.

@@

%Specific things the working group wants to accomplish in the context of the larger objective.
This group is interested in reducing the burden of different projects having to build and maintain their own continuous integration systems, by coordinating and sharing this burden across multiple projects.

@@

How could a reader get more information or get more involved?

>>>>

%Introduction to group here, including the overall objective of work in this area.
Each developer of software with uncommon needs (hardware, software, libraries, data sets) or non-public code must acquire, setup, and maintain their own continuous integration systems because their needs make them ineligible for popular free services such as Travis CI.  For example, software groups that develop BIOUNO, CI4SI, GROMACS) have done this.

@@

%Specific things the working group wants to accomplish in the context of the larger objective.
This group is interested in reducing the burden of different projects having to build and maintain their own continuous integration systems (when publicly available CI are not a fit), by coordinating and sharing this burden across multiple projects.

@@

https://groups.google.com/forum/#!forum/continuous-integration-for-research-software
